Title

### 2013-03-19 inc/design_considerations/considerations.tex
rename some sections remove "experimental results" section (unused)
added large $\Delta x$ limitation to considerations

\section{Pulse Charge Requirements}

It is easy to believe that in order to make a useful image in an electron microcope, the number of electrons collected must be above some minimum number.
The Rose criterion \cite{rose_television_1948} indicates that an average detector signal strength of $\sim$100 electrons/pixel is required for adequate gray scaling of the image.
For a 1k x 1k CCD camera, this implies an incident electron pulse with $N=10^8$ \cite{armstrong_prospects_2007}.

@@

>>>>

\section{Pulse Charge Requirement}

It is easy to believe that in order to make a useful image in an electron microcope, the number of electrons collected must be above some minimum number.
The Rose criterion \cite{rose_television_1948} indicates that an average detector signal strength of $\sim$100 electrons/pixel is required for adequate gray scaling of the image.
For a 1k $\times$ 1k CCD camera, this implies an incident electron pulse with $N=10^8$ \cite{armstrong_prospects_2007}.

@@

\section{Generation Current Limitations}

Since we are now aware that there is a large minimum number of electrons needed per pulse, it is only natural to ask if there is the practical limit on how much charge (i.e., the number of electrons/pulse, $N$) can be extracted from a pulsed laser-driven DC photoelectron gun.
When the incident laser pulse duration $\tau$ is longer than the time-of-flight (TOF) $t_{gun}$ of a single electron across the acceleration gap $d$ of the DC gun with a potential $V_{DC}$, $\tau > t_{gun} = d \sqrt{2m/eV_{DC}}$, then the maximum photocurrent density $J_{CL}$ is given by the well-known Child-Langmuir law \cite{child_discharge_1911,langmuir_effect_1923}:
\begin{equation}
  J_{CL} = \frac{4 \varepsilon_0}{9} \sqrt{\frac{2e}{m}} \frac{V_{DC}^{3/2}}{d^2}
\end{equation}
where $e$ is the electron charge and $\varepsilon_0$ is the vacuum permittivity.

This steady-state law for the maximum current density that can be achieved is not valid in the regime of interest for UEM (and UED) where the use of picosecond and femtosecond photocathode drive laser pulses implies that $t_{gun}$ is usually much greater than the electron pulse duration $\tau_e$.
In fact, though there is no clear definition in the literature or the community, we propose that this is useful delimination between term UEM and the more general term DTEM; reserving the term UEM for when the pulse can be completely contained inside the accelerator, i.e. $t_{gun} > \tau_e$.
In this short pulse case, an equivalent diode approximation \cite{valfells_effects_2002} allows for the definition of a critical current density associated with virtual cathode formation in terms of the steady-state Child-Langmuir limit:
\begin{equation}
  J_{crit} = \frac{27}{4} \left ( \frac{ 1 - \sqrt{1-\tfrac{1}{3} \chi^2} }{ \chi^3 } \right ) J_{CL}
\end{equation}
where $\chi = \tau_e / t_{gun}$.
Thus, for the usual case in UEM, where $\chi \ll 1$, the critical current density is simply given by
\begin{equation}
  J_{crit} = \frac{\varepsilon_0 E_{DC}}{\tau_e}
\end{equation}
where the DC gun field $E_{DC} = V_{DC}/d$.
This relation may be rewritten to yield a critical number of photoemitted electrons/pulse before virtual cathode formation:
\begin{equation} \label{eq:n_crit}
  N_{crit} = \frac{\pi \varepsilon_0 w^2 V_{DC}}{e d}
\end{equation}
In obtaining the above equation, we have used an irradiated photocathode area of $\pi w^2$ associated with an incident Gaussian laser pulse of the form of \ref{eq:laser_form}.
The relation clearly indicates that $N_{crit}$ is only dependent upon the initial DC surface field (i.e., $E_{DC}$) at the photocathode and the illuminated area --- as expected because a virtual cathode forms when the initial photocathode surface charge density associated with $E_{DC}$ is photoemitted, effectively screening the cathode from the acceleration field.

For a typical DC gun with $E_{DC} \approx $ 30 kV/cm (e.g., $V_{DC} = $ 100 kV and $d \approx $ 3 cm), \ref{eq:n_crit} reveals that the generation of $10^8$ electrons/pulse needed for single-shot imaging applications in a DTEM with a 1k $\times$ 1k CCD detector requires an incident laser beam area $\pi w^2$ of about 1 mm$^2$ --- the virtual cathode being formed for the extraction of more than $1.7 \times 10^8$ electrons/mm$^2$ in this short pulse regime.
We note that \ref{eq:n_crit} does not express a limit on the number of electrons/pulse $N$ that can be emitted from a pulsed laser-driven DC photoelectron gun, it merely indicates a critical number before virtual cathode formation occurs.
More electrons can be produced, at the expense of a severely distorted temporal electron pulse profile \cite{valfells_effects_2002}.

This finally leads to the first consideration for UEM design mentioned in the introduction: for the clean pulsed emission of sufficient to create a useful image, the generated beam should have a HW1/eM width 
\begin{equation}
  w \gtrsim \sqrt{\frac{N e d}{\pi \varepsilon_0 V_{DC}}} \,\text{.}
\end{equation}
For our example case of a 1k $\times$ 1k CCD, $N \ge 10^8$ electrons/pulse, we require $w \gtrsim $ 0.56 mm.

\section{Beam Quality and Resolution Limit}
